Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Some sentence restructuring in the conclusion for more clarity.

	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is no system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting some things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.

>>>>

	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor. Decentralized systems that do exist such as Tarzan, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet. Yet each of these systems either lacks in performance or is vulnerable to some type of attack.
